The \dealii{} Library, Version 9.3

### 2021-06-19 9.3/paper.tex
step-74 description

\item \texttt{step-74} SIPG for the Poisson equation \todo[inline]{TODO}

>>>>

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
in combination with \texttt{MeshWorker::mesh\_loop()}. With \texttt{FEInterfaceValues},
we can directly obtain the jump and the average of shape functions and of the solution 
across cell faces, which simplifies the assembling of face terms in DG methods especially on 
adaptive meshes.
